%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Alok}{Kumar Patel}
{ \urlstyle{same} +91 7250723796 | \href{mailto:kumaralok344@gmail.com}{kumaralok344@gmail.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{KIIT University}
\descript{BTech in Computer Science}
\location{Oct 2024 | Bhubaneswar, Odisha}
\location{ CGPA: 7.9}
\sectionsep

\subsection{D.A.V. Public School, Sec- 4}
\descript{INTERMEDIATE}
\location{2020 | Bokaro Steel City, JH}
\location{ CGPA: 7.2}
\sectionsep

\subsection{Chinmaya Vidyalaya}
\descript{HIGH SCHOOL}
\location{2018 | Bokaro Steel City, JH}
\location{ CGPA: 7.4}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/4-alok}{\bf 4-alok} \\
YouTube://  \href{https://www.youtube.com/@4_alokk}{\bf @4\_alokk} \\
Stackoverflow://  \href{https://stackoverflow.com/users/13206009/alok-kumar}{\bf alok-kumar}\\
LinkedIn://  \href{https://www.linkedin.com/in/4-alok}{\bf 4-alok} \\
Twitter://  \href{https://twitter.com/4_alokk}{\bf @4\_alokk} \\
Insta:// \href{https://iinstagram.com/4_alokk}{\bf@4\_alokk}\\
Facebook:// \href{https://www.facebook.com/01alok}{\bf 01alok}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Data Structures Algorithm\\
AI/ML\\
Natural language processing\\
Cloud Computing\\
Operating Systems\\
DBMS\\
Big Data\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 100K+ lines:}
\textbf{Flutter: }GetX framework |Clean
Architecture |freezed |hive |animation\\BLOC |http |Firebase |Provider \\Unit test |Mockito |more...\\
\location{Over 10k+ lines:}
\textbf{AI/ML: }Numpy |Pandas |Matplotlib\\Seaborn |Scikit learn |nltk |TensorFlow |Keras |torch\\
\textbf{Familiar: }os |google.oauth2\\googleapiclient | more...\\
\textbf{Graphic: }Adobe XD |Photoshop |After Effect |Primer Pro |Figma |Blender\\Google SketchUP |Unreal Engine 4\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\runsubsection{KYLO APPS}
\descript{| Flutter Developer}
\location{Apr 2022 - May 2022 | Remote}
\begin{tightemize}
\vspace{\topsep}
\item Created over 30+ screens and integrating QR scanning and deep linking features.
\item Successfully connected API endpoints to ensure seamless app functionality.
\item Created a user-friendly and visually appealing interface based on provided design.
\end{tightemize}
\sectionsep

\runsubsection{Vulmiqi}
\descript{| Flutter Developer }
\location{Dec 2021 – Mar 2022 | Remote}
\begin{tightemize}
\item Developed a Flutter-based visiting card app for multiple businesses at Vulmiqi.
\item Created an intuitive and user-friendly interface to facilitate seamless navigation and usage.
\item Employed best practices to ensure app functionality and stability.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project Experience}

% \datecolor{April 2021} \runsubsection{Recite: Text-to-speech app for web & PDF}
% \descript{}
% \noindent
% \hspace{5em}%
% \begin{minipage}{0.85\textwidth\vspace{2pt}}
% Created a feature-rich text-to-speech programme with sophisticated functions such as PDF integration, NLP-based phrase detection, and Google TTS implementation.
% Implemented complex UI components and managed caching for optimal performance.
% Reached 10,000+ downloads.
% \end{minipage}
% \descriptright{Flutter, Dart, Kotlin, Java}

\runsubsection {Recite: Text-to-speech app}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{10}{12}\selectfont \textbf{Led the team} in developing a feature-rich text-to-speech app with sophisticated functions such as \textbf{PDF integration, NLP-based phrase detection, and Google TTS} implementation. Implemented complex UI components and managed caching for optimal performance.
Reached \textbf{10,000+} downloads.}
\end{tightemize}
\descriptright{Flutter, Dart, Kotlin, Java}
\sectionsep

\runsubsection{Class Link}\hfill {open source}
% \descript{open source}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{10}{12}\selectfont A fully production level app with a user-friendly UI that allows users to view their current class with just one click, access holidays list, resources (notes and PYQs), and more. Over \textbf{3K+ active users} opening the app approximately 5 times a day. Features include a great user-friendly UI, easy access to current class, holidays list, resources, and more.
\end{tightemize}
\descriptright{Flutter, Dart, Python, Go}
\sectionsep

\runsubsection{draggable\_home}\hfill {open source}
% \descript{open source}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{10}{12}\selectfont Created and maintained a popular Flutter package, draggable\_home for implementing sliding up and fully-stretchable features. Received \textbf{400+ likes on pub.dev} and gained \textbf{100+ stars} on GitHub for the "draggable\_home" package. Currently used by \textbf{170+ projects}, showcasing its popularity and wide adoption in the Flutter community.
\end{tightemize}
\descriptright{Flutter, Dart}
\sectionsep

\sectionsep
\runsubsection {file\_manager}\hfill {open source}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{10}{12}\selectfont Developed FileManager package for Flutter with \textbf{100+ likes} on pub.dev and \textbf{50+ stars} on GitHub. Created intuitive widget for file and folder management, seamlessly integrating with Flutter framework. Used by over \textbf{100} developers, providing powerful file management features for Flutter applications.
\end{tightemize}
\descriptright{Flutter, Dart}
\sectionsep

\sectionsep
\runsubsection {DevsOnFlutter : Flutter Open-Source Community}\\
\location{June 2021 - Present}
\vspace{\topsep}
\begin{tightemize}
{\fontsize{10}{12}\selectfont I created and manage the \textbf{DevsOnFlutter Github page}, which is a popular open-source community for Flutter developers. With a demonstrated expertise in working with and \textbf{contributing to open-source} projects related to Flutter, I am recognized in the Flutter community for my contributions and expertise.
\end{tightemize}
\sectionsep


% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %     RESEARCH
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
% \location{Jan 2014 – Jan 2015 | Ithaca, NY}
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  
% \sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% 2013	     & National  & Jump Trading Challenge Finalist\\
% 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\

% \end{tabular}
% \sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     PUBLICATIONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
